BAI resiliences ten droughts

### 2019-05-27 analysis/bai/trends_resilience_bai.Rmd
update

```{r}
bai_sj <- bai_piovesan(rwdf = sj_tree, diam_df = d_sj)
bai_caH <- bai_piovesan(rwdf = caH_tree, diam_df = d_caH)
bai_caL <- bai_piovesan(rwdf = caL_tree, diam_df = d_caL)

@@

@@

>>>>

```{r}
sj_tree <- subset(sj_tree, select=-c(nseries))
caH_tree <- subset(caH_tree, select=-c(nseries))
caL_tree <- subset(caL_tree, select=-c(nseries))

bai_sj <- bai_piovesan(rwdf = sj_tree, diam_df = d_sj)
bai_caH <- bai_piovesan(rwdf = caH_tree, diam_df = d_caH)
bai_caL <- bai_piovesan(rwdf = caL_tree, diam_df = d_caL)

@@

```{r}
# Variante todos juntos 
resi_temporal_one <- s %>% filter(samps >= 10) %>% 
  ggplot(aes(y=rs_mean, x=disturb_year, colour=site)) + 
  geom_errorbar(aes(ymin=rs_mean - rs_sd, 
                    ymax=rs_mean + rs_sd),
                width = 0.75, 
                size = .7,
                position=position_dodge(2)) +
  geom_point(aes(size=d_severity), shape=21, fill='white', position=position_dodge(2)) +

  # facet_wrap(~site, scales='free_y', ncol=1) + 
  theme_bw() + 
  theme(strip.background = element_rect(fill='transparent'), 
        panel.grid.minor = element_blank(),
        panel.grid.major.x = element_blank()) + 
  ylab('Resilience (Rs)') + xlab('years') + 
  scale_x_continuous(breaks=seq(1910,2020, by=5)) # + geom_smooth(aes(colour=site), se=FALSE)

resi_temporal_one

pdf(here::here('/out/bai_resiliences_severes', 'res_bai_longterm_one.pdf'), width=12, height = 9)
resi_temporal_one
dev.off()
```

@@

```{r sin_95}
sdf95 <- sdf %>% filter(disturb_year != 1995)

sevRt95 <- plotrel(sdf95, v = "rt", x = 'd_severity', label = 'disturb_year',
                 coordX_eq = 6, coordY_eq = 0.5, titulo = "Rt") +
  xlab('') + ylab('') +
  theme(plot.margin = margin(r=-0.7, l=0, t=0, b=0, "pt"))

sevRs95 <- plotrel(sdf95, v = "rs", x = 'd_severity', label = 'disturb_year',
                 coordX_eq = 6, coordY_eq = 0.5, titulo = "Rs") + 
  xlab('') + ylab('') +
  theme(plot.margin = margin(r=0, l=-0.7, t=0, b=0, "pt"))

sevRc95 <- plotrel(sdf95, v = "rc", x = 'd_severity', label = 'disturb_year',
                 coordX_eq = 6, coordY_eq = 0.5, titulo = "Rc") +
  xlab("Drought Severity") + ylab('') +
  theme(plot.margin = margin(r=-0.7, l=-0.7, t=0, b=0, "pt"))

res_long_term95 <- sevRt95 + sevRc95 + sevRs95 + 
  plot_layout(nrow = 1)

res_long_term95

pdf(here::here('/out/bai_resiliences_severes', 'rs_vs_drought_3years_95.pdf'), width=18, height = 7)
res_long_term95
dev.off()
